Kepler's Demographic Cliff: Ages of Young Stars and Planets in the Kepler Field

### 2024-05-08 paper/ms.tex
update ms

{\it Near the main-sequence (bit 9)}---Many stars observed by Kepler
are far from the main sequence: this can be seen in color--absolute
magnitude diagrams, and in diagrams of e.g.~surface gravity as a
function of temperature (Figure~\ref{fig:stellarprops}).  This is a
challenge for rotation-based ages because {\it i)} point sources
far from the main-sequence include unresolved photometric binaries,
and {\it ii}) effects other than magnetic braking influence the
rotation periods of bona fide single stars far from the main-sequence.
The added complications of reddening and metallicity further
complicate matters.  
After exploring various options, we settled on the orange locus in the
$\log g$--$T_{\rm eff}$ plane shown in Figure~\ref{fig:stellarprops}.
While the details of how exactly this locus is constructed are
arbitrary and convoluted,\footnote{In practice, for K dwarfs we fitted an
$N^{\rm th}$-order polynomial to the set of stars for which $t_{\rm
B20,iso}/(+\sigma_{t,{\rm B20,iso}})\approx 3$, where
$t_{\rm B20,iso}$ was the isochronal age reported by
\citet{Berger_2020a_catalog}. We let the order of the fit vary from
$N$=1 to 10, minimized the Bayesian Information Criterion,
and found $N$=6.  For F and G dwarfs, this procedure failed to produce
a reasonable locus because of shifts in the relative precision of
the isochrone ages.  We therefore visually selected KOIs that appeared
to be near the ``main sequence'', fitted a separate polynomial to
their locations, and then stitched the resulting polynomials from the
F and G dwarfs to that of the K dwarfs.} the general 
aim is to exclude stars for which there is photometric evidence
that gyrochronology may not be reliable.  The rotation period
distribution of sources excluded in this manner includes a relatively
larger fraction of ``rapid rotators'' than the main sequence sources,
likely due to a combination of astrophysical and systematic effects.
See for instance Figure~8a of \citet{2022AJ....164..137K} or Figures~12 and 13
of \citet{2023ApJS..268....4F}.

@@

\begin{figure*}[!p]
  \begin{center}
    \leavevmode
    \subfloat{
    \includegraphics[width=\textwidth]{comp_hist_samples_koi_gyro_ages_hist_field_gyro_ages_20240430_maxage4000.pdf}
    }

	\vspace{-0.3cm}
    \subfloat{
    \includegraphics[width=\textwidth]{comp_hist_samples_koi_gyro_ages_hist_field_gyro_ages_20240430_maxage4000_preciseagesonly.pdf}
    }
  \end{center}
  \vspace{-0.6cm}
  \caption{
    {\bf Kepler's demographic cliff,} visible in the rotation-derived
    ages of stars (left) and planet hosts (middle) in the Kepler field.
    The top row corresponds to all
    stars with $T_{\rm eff}\in[3800,6200]\,$K for which we calculated rotation-based ages.
    The darker lines impose quality cuts
    on factors such as binarity, crowding, and the star's evolutionary
    state.
    The bottom row selects only stars with $T_{\rm eff}\in[4400,5400]\,$K, which
    have relatively precise ages near 2\,Gyr due to their fast spin-down
    \citep[see][]{Bouma_2023}.
    The statistical uncertainty for a mean individual star at 1, 2, and 3\,Gyr is shown, and is identical across each row.
    Finally, the right panel compares the rotation-based age distributions against star formation histories derived using CMD fitting.
    Completeness is near unity until $t$$\lesssim$3\,Gyr
    \citep{2022ApJ...937...94M}.
    \label{fig:hist_tgyro}
  }
\end{figure*}

@@

\begin{figure*}[!t]
  \begin{center}
    \includegraphics[width=0.85\textwidth]{rp_vs_period_scatter_20240415_colorbyage_showaux-gyro_anyyoung_anyyoung.pdf}
  \end{center}
  \vspace{-0.5cm}
  \caption{
    {\bf Sizes, orbital periods, and rotation-based ages of transiting
    exoplanets younger than one billion years.} Stars denote
    \nplyounggyrotwosigmanograzingnoruwe\ planets that are newly
    characterized in this work to have $t_{\rm gyro}$<1\,Gyr at
    $2$$\sigma$; circles are planets from the literature meeting the
    same age requirement, but with a heterogeneous set of age
    provenances.  Gray points are transiting planets from the NASA
    Exoplanet Archive older than 1\,Gyr.  If one were to instead select for
    precise ages ($t/\sigma_{\rm t}>3$), this would hide $\approx$ten
    $<$0.5\,Gyr planets, and add $\approx$fifteen 0.5-1\,Gyr planets.
    For this plot, we require our Kepler stellar hosts to have no
    quality flags raised, and for the planets to
    similarly no have quality flags raised. 
    \label{fig:rp_period_age_results}
  }
\end{figure*}

@@

\subsubsection{New Young Systems}
%
Whenever both rotation and lithium find a star to be in a
narrowly-constrained age range, confidence in the true age
increases, because the two techniques are independent.
The region of greatest overlap between rotation and lithium ages in
the spaces of $P_{\rm rot}$, EW$_{\rm Li}$, and $T_{\rm eff}$ is
dictated by the timescale for lithium depletion: for stars with
temperatures between 4500-5500\,K with ages $\lesssim$1\,Gyr, we can
hope to obtain independent two-sided constraints
\citep{Bouma_2023,Jeffries_2023}.

The following systems, to our knowledge, are being
well-constrained for the first time in this work.  Here we limit
discussion to systems with $t_{\rm gyro}$$<$500\,Myr not in the clusters
mentioned above.
{\bf FIXME TODO: next two paragraphs are boring.  come up with a better way to do this,
and maybe automate}

The new young planets
include five 1.8-3.8\,$R_\oplus$ mini-Neptunes
(Kepler-1529b $\approx$100\,Myr,
-1521b $\approx$195\,Myr,
-1467b $\approx$235\,Myr,
-955b $\approx$400\,Myr, and
-523b $\approx$440\,Myr),
a single Neptune-sized planet
(Kepler-971b $\approx$335\,Myr),
five 1.1-1.8\,$R_\oplus$ super-Earths
(Kepler-1930b $\approx$150\,Myr,
-1313b $\approx$185\,Myr,
-1565b $\approx$205\,Myr,
-1532b $\approx$400\,Myr,
-1481b $\approx$400\,Myr),
and three Earth or sub-Earth-sized planets
(Kepler-1933b $\approx$300\,Myr,
-1561b $\approx$420\,Myr,
-1482b $\approx$490\,Myr).
All of these planets are on orbital periods below 50\,days.

Of these planets, one specific highlight is Kepler-1933b, a 4.9\,day
1.0\,$R_\oplus$ Earth-sized planet.  Its rotation-based age of
$304^{+96}_{-112}$\,Myr agrees within $1\sigma$ of its lithium age,
though at half the relative uncertainty.  This system may be the
youngest Earth-sized planet currently known, comparable to systems
such as HD~63433d \citep[1.1\,$R_\oplus$,
$414\pm23$\,Myr][]{2024AJ....167...54C}.

A less clear case is Kepler-447b, which is supposedly a 32\,$R_\oplus$
planet on a 7.8\,day grazing orbit.  Rotation and lithium independently
find a 420-440\,Myr age.  {\it LGB TODO What is up with the size?}.

@@

Most of the stars observed by Kepler are in the Galaxy's thin disk.
This can be verified by following \citet{Gaia_2018}, and denoting stars with 2D tangential
velocities $v_{\rm T}$$<$40\,\kms\ as thin disk members, and those
with 60$<$$v_{\rm T}$$<$150\,\kms as thick disk members.  For all
stars in the KIC, this yields 95{,}694 thin and 54{,}039 thick disk stars respectively.  
The thin disk stars have a threefold larger detected rotation period
fraction: 35{,}675 rotators are in the thin disk, while 7{,}312 are in
the thick disk.  Further imposing the gyrochronology quality flags
discussed in Section~\ref{subsec:flags} yields 17{,}755
thin-disk stars for which gyrochronology is nominally applicable, and
2{,}462 thick-disk stars.

The kinematic distinction between thin and thick disk stars helps connect
the Kepler stars to the broader literature focused
on the history of star formation in the Galaxy.  On extragalactic
scales, the star formation rate in spiral galaxies with mass
comparable to the Milky Way peaked $\approx$10\,Gyr ago, and has since
decreased by about an order of magnitude
\citep[e.g.][]{2004Natur.428..625H,2006ApJ...651..142H}.  For our own
galaxy, many investigators have worked to measure similar star
formation histories, through both CMD fitting of resolved stellar
populations
\citep[][]{2019A&A...624L...1M,2020NatAs...4..965R,2021MNRAS.501..302A,2022Natur.603..599X}
and also by modelling the local white dwarf luminosity function
\citep[e.g.][]{2019ApJ...878L..11I}.  
\citet{2019A&A...624L...1M} and \citet{2019ApJ...878L..11I} for
instance focused on stars (and white dwarfs) within a few hundred
parsecs, and both reported a local maximum in the galactic star
formation rate 2-3\,Gyr ago.  \citet{2020NatAs...4..965R} focused on
stars in a wider 2\,kpc bubble, and reported three local maxima
in the thin disk's star formation history 5.7, 1.9, and 1.0\,Gyr ago,
which they associate with pericenter passages of the Sagittarius satellite
galaxy.

@@

Most ages reported in this study come from a single source of information: rotation.
Factors other than stellar age and mass can influence rotation rates of main sequence stars.
Binarity is the best example of this: even intermediate-separation ($\sim$10\,AU) binaries are biased
toward rotating anomalously
rapidly
\citep{Meibom_2007,2016AJ....152..115S,2019ApJ...871..174S,Gillen_2020,Bouma_2021}.
Metallicity may also be a second-order effect
\citep{2020MNRAS.499.3481A,2024arXiv240500779S}.
In this work, we were interested in not only the overall
age distribution of the Kepler field, but also in the reliability of ages for
individual young planet hosting stars.
The quality flagging scheme in Table~\ref{tab:planets} provides one method in support of
this end.
The other method is to consider the region in which we do have
overlapping sensitivity between lithium and rotation -- 
G and K dwarfs with $t$$\lesssim$1\,Gyr.  
Our results for such stars include
\ltonegyrhighqconfirmedtwosided\ planets orbiting ``high-quality''
stars for which the two age indicators are both constraining and in agreement
(with $Q_{\rm gyro}$ bits zero through nine not raised, and no planet quality flags raised).
Conversely, we found only one system, Kepler-786, with a clearly
constraining lithium age (\kepseveneightsix\,Myr) and no rotation age.

@@

We began this article by asking two questions: how wrong is the
assumption of a uniform age distribution for stars in the galactic
thin disk?  And why are only $\approx$50 sub-gigayear transiting
planets known, rather than the $\approx$500 that would be expected
under the assumption of a uniform star formation history for the
$\approx$5{,}000 known planets?

In an attempt to answer these questions, we curated a sample of
rotation periods, lithium equivalent widths, and stellar temperatures
using a combination of archival and new data.  We derived new ages
using empirical interpolation-based age scales that have been
calibrated against the latest available open cluster data.

Our analysis blindly recovered all 14 known Kepler planets in
clusters, with ages in agreement with the more precise cluster-based
ages.  Although lithium provided only marginal added information for
most of the sample, the independent lithium and rotation ages agreed
for $\approx$90\% of cases.  In particular, we reported 14 confirmed
$<$500\,Myr planets with strong age constraints from both rotation and
lithium, including five mini-Neptunes, five super-Earths, three Earths
and sub-Earths, and a Neptune-sized planet.

@@

\clearpage

@@

\section{Notable Individual Systems}

>>>>

{\it Near the main-sequence (bit 9)}---Many stars observed by Kepler
are far from the main sequence: this can be seen in color--absolute
magnitude diagrams, and in diagrams of e.g.~surface gravity as a
function of temperature (Figure~\ref{fig:stellarprops}).  This is a
challenge for rotation-based ages because {\it i)} point sources
far from the main-sequence include unresolved photometric binaries,
and {\it ii}) effects other than magnetic braking influence the
rotation periods of bona fide single stars far from the main-sequence.
The added complications of reddening and metallicity further
complicate matters.  
After exploring various options, we settled on the orange locus in the
$\log g$--$T_{\rm eff}$ plane shown in Figure~\ref{fig:stellarprops}.
While the details of how exactly this locus is constructed are
arbitrary, 
%and convoluted,\footnote{In practice, for K dwarfs we fitted an
%$N^{\rm th}$-order polynomial to the set of stars for which $t_{\rm
%B20,iso}/(+\sigma_{t,{\rm B20,iso}})\approx 3$, where
%$t_{\rm B20,iso}$ was the isochronal age reported by
%\citet{Berger_2020a_catalog}. We let the order of the fit vary from
%$N$=1 to 10, minimized the Bayesian Information Criterion,
%and found $N$=6.  For F and G dwarfs, this procedure failed to produce
%a reasonable locus because of shifts in the relative precision of
%the isochrone ages.  We therefore visually selected KOIs that appeared
%to be near the ``main sequence'', fitted a separate polynomial to
%their locations, and then stitched the resulting polynomials from the
%F and G dwarfs to that of the K dwarfs.}
the general 
aim is to exclude stars for which there is evidence 
based on their location in the $\log g$--$T_{\rm eff}$ plane
that our gyrochronology model may not be reliable.  
%The rotation period
%distribution of sources excluded in this manner includes a relatively
%larger fraction of ``rapid rotators'' than the main sequence sources,
%likely due to a combination of astrophysical and systematic effects.
See for instance Figure~8a of \citet{2022AJ....164..137K} or Figures~12 and 13
of \citet{2023ApJS..268....4F} for examples of how this period distribution
of this population differs from stars near the main sequence.

@@

\begin{figure*}[!t]
  \begin{center}
    \leavevmode
    \subfloat{
    \includegraphics[width=\textwidth]{comp_hist_samples_koi_gyro_ages_hist_field_gyro_ages_20240430_maxage4000.pdf}
    }

	\vspace{-0.35cm}
    \subfloat{
    \includegraphics[width=\textwidth]{comp_hist_samples_koi_gyro_ages_hist_field_gyro_ages_20240430_maxage4000_preciseagesonly.pdf}
    }
  \end{center}
  \vspace{-0.6cm}
  \caption{{\bf Kepler's demographic cliff,} visible in the rotation-derived
    ages of stars (left) and planet hosts (middle) in the Kepler field.
    The top row corresponds to all
    stars with $T_{\rm eff}\in[3800,6200]\,$K for which we calculated rotation-based ages.
    The darker lines impose quality cuts
    on factors such as binarity, crowding, and the star's evolutionary
    state.
    The bottom row selects only stars with $T_{\rm eff}\in[4400,5400]\,$K, which
    have relatively precise ages near 2\,Gyr due to their fast spin-down
    \citep[see][]{Bouma_2023}.
    The statistical uncertainty for a mean individual star at 1, 2, and 3\,Gyr is shown, and is identical across each row.
    Finally, the right panel compares the rotation-based age distributions against star formation histories derived using CMD fitting.
    Completeness is near unity until $t$$\lesssim$3\,Gyr
    \citep{2022ApJ...937...94M}.
    \label{fig:hist_tgyro}
  }
\end{figure*}

@@

\begin{figure}[!t]
  \begin{center}
    \includegraphics[width=0.48\textwidth]{rp_vs_period_scatter_20240415_colorbyage_showaux-gyro_anyyoung_anyyoung.pdf}
  \end{center}
  \vspace{-0.5cm}
  \caption{
    {\bf Sizes, orbital periods, and rotation-based ages of transiting
    exoplanets younger than one billion years.} Stars denote
    \nplyounggyrotwosigmanograzingnoruwe\ planets that are newly
    characterized in this work to have $t_{\rm gyro}$<1\,Gyr at
    $2$$\sigma$; circles are planets from the literature meeting the
    same age requirement, but with a heterogeneous set of age
    provenances.  Gray points are transiting planets from the NASA
    Exoplanet Archive older than 1\,Gyr.  If one were to instead select for
    precise ages ($t/\sigma_{\rm t}>3$), this would hide $\approx$ten
    $<$0.5\,Gyr planets, and add $\approx$fifteen 0.5-1\,Gyr planets.
    For this plot, we require our Kepler stellar hosts to have no
    quality flags raised, and for the planets to
    similarly no have quality flags raised. 
    \label{fig:rp_period_age_results}
  }
\end{figure}

@@

\subsubsection{New Young Systems}
%
%The astrophysical processes behind rotation and lithium evolution are
%independent.
%Therefore 
%whenever the two age indicators agree within a
%narrowly-constrained range, confidence in the true age
%increases.
%The region of greatest overlap between rotation and lithium ages is
%dictated by the timescale for lithium depletion: for stars with
%temperatures between 4500-5500\,K with ages $\lesssim$1\,Gyr, we can
%hope to obtain independent two-sided constraints
%\citep{Bouma_2023,Jeffries_2023}.

Let us restrict our attention to blemish-free stars, with blemish-free
``confirmed'' planets:
$Q_{\rm gyro}$ must not have any of bits zero through nine
raised, and $Q_{\rm planet}$ must have no quality flags raised at all.
Under this constraint,
our results include \ltonegyrhighqconfirmedtwosided\ systems
younger than 1\,Gyr with two-sided $t_{\rm gyro}$ and $t_{\rm Li}$,
and \ltonegyrhighqconfirmedonesided\ cases for which $t_{\rm gyro}$ provides
an age constraint while $t_{\rm Li}$ is one-sided.
%Two of the former systems are in clusters (Kepler-1643 and Kepler-1928);
%five of the latter systems are in Theia~520.

These planets are shown in Figure~\ref{fig:rp_period_age_results}.
They include \nearthshighqconfirmed\ Earth-sized or smaller planets,
no Jupiter-sized or larger planets,
\nsubsaturnshighqconfirmed\ ``super-Neptune'' ($>$4\,$R_\oplus$) sized
planets,
\nminineptuneshighqconfirmed\ mini-Neptunes above the 
radius valley (as parametrized by \citealt{2018MNRAS.479.4786V}),
and \nsuperearthshighqconfirmed\ super-Earth sized planets below the radius valley.
While most of these planets are on orbital periods below 50\,days,
\nlongperiodhighqconfirmed\ are on more distant orbits.

%The new young planets
%include five 1.8-3.8\,$R_\oplus$ mini-Neptunes
%(Kepler-1529b $\approx$100\,Myr,
%-1521b $\approx$195\,Myr,
%-1467b $\approx$235\,Myr,
%-955b $\approx$400\,Myr, and
%-523b $\approx$440\,Myr),
%a single Neptune-sized planet
%(Kepler-971b $\approx$335\,Myr),
%five 1.1-1.8\,$R_\oplus$ super-Earths
%(Kepler-1930b $\approx$150\,Myr,
%-1313b $\approx$185\,Myr,
%-1565b $\approx$205\,Myr,
%-1532b $\approx$400\,Myr,
%-1481b $\approx$400\,Myr),
%and three Earth or sub-Earth-sized planets
%(Kepler-1933b $\approx$300\,Myr,
%-1561b $\approx$420\,Myr,
%-1482b $\approx$490\,Myr).

A few new highlights from the high quality stars and planets include
Kepler-1529, Kepler-1565, Kepler-1312, and Kepler-1629.
Kepler-1529b is a $\approx$100$\pm$50\,Myr mini-Neptune with well-measured
rotation and lithium ages.
Kepler-1565b is an analogous $\approx$170-230\,Myr super-Earth.
Kepler-1312 is a $t_{\rm gyro}$=\kepthirteentwelve\,Myr near-Solar analog with
two known transiting planets: an Earth-sized planet on a one-day orbit,
and a mini-Neptune on a five-day orbit.
The Earth-sized planet, Kepler-1312c, along with the near-identical
Kepler-1561 b ($t_{\rm gyro}$=\kepfifteensixone\,Myr), 
could be the
youngest Earth-sized planets currently known, comparable to systems
such as HD~63433d \citep[1.1\,$R_\oplus$,
$414$$\pm$$23$\,Myr;][]{2024AJ....167...54C} and TOI-1807~b \citep[1.3\,$R_\oplus$, 180$\pm$40\,Myr;][]{2021AJ....162...54H}.
Kepler-1629~b, with a size just two-thirds that of Earth
(0.67$\pm$0.05\,$R_\oplus$), is marginally older, also based on rotation
(\kepsixteentwonine\,Myr).  The lithium age from a reconnaissance 
TRES spectrum confirms the point.

%Of these planets, one specific highlight is Kepler-1933b, a 4.9\,day
%1.0\,$R_\oplus$ Earth-sized planet.  Its rotation-based age of
%$304^{+96}_{-112}$\,Myr agrees within $1\sigma$ of its lithium age,
%though at half the relative uncertainty.

%A less clear case is Kepler-447b, which is supposedly a 32\,$R_\oplus$
%planet on a 7.8\,day grazing orbit.  Rotation and lithium independently
%find a 420-440\,Myr age.  {\it LGB TODO What is up with the size?}.

@@

Most of the stars observed by Kepler are in the thin disk.
This can be verified by following \citet{Gaia_2018}, and denoting stars with 2D tangential
velocities $v_{\rm T}$$<$40\,\kms\ as thin disk members, and those
with 60$<$$v_{\rm T}$$<$150\,\kms as thick disk members.  For all
stars in the KIC, this yields 95{,}694 thin and 54{,}039 thick disk stars respectively.  
The thin disk stars have a threefold larger detected rotation period
fraction: 35{,}675 rotators are in the thin disk, while 7{,}312 are in
the thick disk.  Further imposing the gyrochronology quality flags
discussed in Section~\ref{subsec:flags} yields 17{,}755
thin-disk stars for which gyrochronology is nominally applicable, and
2{,}462 thick-disk stars.

Classifying Kepler stars in this manner helps connect
them to the broader literature focused
on the history of star formation in the Galaxy.  On extragalactic
scales, the star formation rate in spiral galaxies with mass
comparable to the Milky Way peaked $\approx$10\,Gyr ago, and has since
decreased by an order of magnitude
\citep[e.g.][]{2004Natur.428..625H,2006ApJ...651..142H}.  For our own
galaxy, many investigators have worked to measure similar star
formation histories, through both CMD fitting of resolved stellar
populations
\citep[][]{2019A&A...624L...1M,2020NatAs...4..965R,2021MNRAS.501..302A,2022Natur.603..599X}
and by modeling the local white dwarf luminosity function
\citep[e.g.][]{2019ApJ...878L..11I}.  
\citet{2019A&A...624L...1M} and \citet{2019ApJ...878L..11I} for
instance focused on stars (and white dwarfs) within a few hundred
parsecs, and both found a peak in the local star
formation rate 2-3\,Gyr ago.  \citet{2020NatAs...4..965R} focused on
stars in a wider 2\,kpc bubble, and reported three local maxima
in the thin disk's star formation history 5.7, 1.9, and 1.0\,Gyr ago,
which they associate with pericenter passages of the Sagittarius satellite
galaxy.

@@

Most of our ages come from a single source of information: rotation.
Factors other than stellar age and mass can influence rotation rates of main sequence stars.
Binarity is one example: even intermediate-separation ($\sim$10\,AU) binaries are biased
toward rapid rotation
\citep[e.g.][and many studies thereafter]{Meibom_2007}. %,2016AJ....152..115S,2019ApJ...871..174S,Gillen_2020,Bouma_2021}.
Metallicity may also be a second-order effect
\citep{2020MNRAS.499.3481A,2024arXiv240500779S}.
In this work, we were interested in not only the overall
age distribution of the Kepler field, but also in the reliability of individual ages for
young planet hosting stars.
The quality flagging scheme in Table~\ref{tab:planets} provides one path toward this end.
The other method is to consider the region in which we do have
overlapping sensitivity between lithium and rotation -- 
G and K dwarfs with $t$$\lesssim$1\,Gyr.  
Our results for such stars include
\ltonegyrhighqconfirmedtwosided\ planets orbiting ``high-quality''
stars for which the two age indicators are both constraining and in agreement
(with $Q_{\rm gyro}$ bits zero through nine not raised, and no planet quality flags raised).
Conversely, we found only one system, Kepler-786, with a clearly
constraining lithium age (\kepseveneightsix\,Myr), but no rotation signal.

@@

We began this article with two questions: how wrong is the
assumption of a uniform age distribution for stars in the galactic
thin disk?  And why are only $\approx$50 sub-gigayear transiting
planets known, rather than the $\approx$500 that would be expected
under the assumption of a uniform star formation history for the
$\approx$5{,}000 known planets?

In an attempt to answer these questions, we curated a sample of
rotation periods, lithium equivalent widths, and stellar temperatures
using archival and new data.  We derived new ages
using empirical interpolation-based methods that have been
calibrated against the latest open cluster data.

Our analysis blindly recovered all 14 known Kepler planets in
clusters, with ages in agreement with the more precise cluster-based
ages.  Although lithium provided only marginal added information for
most of the sample, the independent lithium and rotation ages agreed
for $\approx$90\% of cases.  
%FIXME TODO NUMBERS
In particular, we reported 14 confirmed
$<$500\,Myr planets with strong age constraints from both rotation and
lithium, including five mini-Neptunes, five super-Earths, three Earths
and sub-Earths, and a Neptune-sized planet.

@@

%\clearpage

@@

\section{Notes on Individual Systems}
